\thetitle

### 2021-06-22 writing/paper.tex
Add CRI grant to acknowledgements
ben edits
- delete "see" as in "see sec. 1"; in most places, there's no need for this
  extra direction
- "mix-typed" -> "mixed-typed"
- move ",here ..." clause to directly follow target
- add oxford comma
- plural -> singular b/c pack-lib is the one and only responsible party
- use "--" for Wadler--Findler
- rational-stuff: **A successful** trail
- rational-transient: "and each" -> "and that each" to clarify the assignment
  says two things .... but it's a little strange to say that shallow checking
  is part of what the blame says
- "blame set" -> "blame seq

\author{Christos Dimoulas}
\orcid{0000-0002-9338-7034}
\affiliation{%
  \institution{PLT @ Northwestern University}
  \city{Evanston}
  \state{Illinois}
  \country{USA}
}
\email{chrdimo@northwestern.edu}
\renewcommand{\shortauthors}{Lazarek, Greenmanm Felleisen, Dimoulas}

@@

@@

%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id></concept_id>
%<concept_desc></concept_desc>
%<concept_significance></concept_significance>
%</concept>
%<concept>
%<concept_id></concept_id>
%<concept_desc></concept_desc>
%<concept_significance></concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}

%\ccsdesc[]{}
%\ccsdesc[]{}

%% Keywords
%% comma separated list
%\keywords{}  %% \keywords are mandatory in final camera-ready submission

@@

%% Acknowledgments
\begin{acks}                 
Felleisen and Greenman were partly supported by NSF grant SHF
1763922. Greenman also received support from a CRA-NSF Post-doctoral
fellowship grant. Dimoulas and Felleisen wish to thank Max New for
extensive discussions of the early ideas in this paper. Thanks also to
Robby Findler and Northwestern PLT for their valuable feedback at
various stages of this work.
\end{acks}

>>>>

\author{Christos Dimoulas}
\orcid{0000-0002-9338-7034}
\affiliation{%
  \institution{PLT @ Northwestern University}
  \city{Evanston}
  \state{Illinois}
  \country{USA}
}
\email{chrdimo@northwestern.edu}
\renewcommand{\shortauthors}{Lazarek, Greenman, Felleisen, Dimoulas}

@@

\pagenumbering{gobble}

@@

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007.10011074.10011099.10011693</concept_id>
       <concept_desc>Software and its engineering~Empirical software validation</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10003752.10010124.10010138.10010140</concept_id>
       <concept_desc>Theory of computation~Program specifications</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Empirical software validation}
\ccsdesc[500]{Theory of computation~Program specifications}

%% Keywords
%% comma separated list
\keywords{gradual typing, blame}  %% \keywords are mandatory in final camera-ready submission

@@

%% Acknowledgments
\begin{acks}                 
Felleisen and Greenman were partly supported by NSF grant SHF
1763922.
Greenman also received support from NSF grant 2030859 to the CRA for the
\href{https://cifellows2020.org}{CIFellows} project.
Dimoulas and Felleisen wish to thank Max New for
extensive discussions of the early ideas in this paper. Thanks also to
Robby Findler and Northwestern PLT for their valuable feedback at
various stages of this work.
This paper was supported in part by the NSF grant CNS-1823244.
\end{acks}
